Kindly Bent to Free Us

### 2019-11-22 kindly/lang.tex
Make a pass over the inference section

\cref{sdtyp:split} shows the action of the splitting rules on single
bindings. If $x$'s type is unrestricted, then
the {\sc Both} rule indicates that we can duplicate it.
Similarly, unrestricted borrows can be duplicated according to rule
{\sc Borrow}.
The {\sc Left} and {\sc Right} rules are always applicable and move a binding
either to the left or right environment.
The rules {\sc Susp}, {\sc SuspB} and {\sc SuspS}
split off suspended bindings to
the left while conserving access to the binding on the right.
A suspended binding can later be turned
into a borrow inside a region. Splitting of suspended bindings is
asymmetric. It must follow the order of execution from left to right,
which means that a resource can be used first as a borrow on the left
and then later as a full resource on the right. The {\sc Susp} rule
works with a full resource, the {\sc SuspB}
with a borrow and {\sc SuspS} with a suspended binding.
%
Splitting applies whenever an
expression has multiple subexpressions:  pairs, function applications,
and let bindings. In the
expression
$\letin{a}{\text{create}\ 10\ x}
{\introPair{\region[{}]{\Sone x\IBORROW}{\app{\text{length}}{\borrow[\IBORROW]{a}}}}{a}}$,
the rule {\sc Susp} splits off a borrow from  the resource
$a$ to use it in the left component of the pair.
As usual, a borrow cannot be active in the same scope as its resource.
The \emph{region} around its use ensures that the borrow in the left component does not
escape, which brings us to the next topic.

>>>>

\cref{sdtyp:split} shows the action of splitting rules on single
bindings. If $x$'s type is unrestricted, 
rule {\sc Both} indicates that we can duplicate it.
Similarly, unrestricted borrows can be duplicated with rule
{\sc Borrow}.
{\sc Left} and {\sc Right} rules are always applicable and move a binding
either to the left or right environment.
The rules {\sc Susp}, {\sc SuspB} and {\sc SuspS}
split off suspended bindings to
the left while conserving access to the binding on the right.
A suspended binding can later be turned
into a borrow inside a region. Splitting of suspended bindings is
asymmetric. It must follow the order of execution from left to right,
which means that a resource can be used first as a borrow on the left
and then later as a full resource on the right. The {\sc Susp} rule
works with a full resource, the {\sc SuspB}
with a borrow and {\sc SuspS} with a suspended binding.
%
Splitting applies whenever an
expression has multiple subexpressions:  pairs, function applications,
and let bindings. In the
expression
$\letin{a}{\text{create}\ 10\ x}
{\introPair{\region[{}]{\Sone x\IBORROW}{\app{\text{length}}{\borrow[\IBORROW]{a}}}}{a}}$,
the rule {\sc Susp} splits off a borrow from  the resource
$a$ to use it in the left component of the pair.
As usual, a borrow cannot be active in the same scope as its resource.
The \emph{region} around its use ensures that the borrow in the left component does not
escape, which brings us to the next topic.
